%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{pifont} 

\usepackage{fontspec}

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Joshua}{Friedman}{ PhD}{Data Scientist} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
545 1\textsuperscript{st} Ave; Apt 2F
New York, NY 10016
~
\href{mailto:josh.nmr@gmail.com}{josh.nmr@gmail.com}{\color{brown} \ding{41}} 
+1 (213) 537 4331{\color{brown} \ding{37}}
~
\href{https://github.com/jfried23}{GitHub: jfried23}
\section{machine learning}
logistic regression
random forrest
pca
n{\"i}ave bayes
neural network
k-means clustering
\section{science}
computational biology
magnetic resonance
synthetic biology
dna damage repair
\section{recognition}
top 4\% of "data incubator program" applicants 
\end{aside}

%----------------------------------------------------------------------------------------
%	CS SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{programming}

\textbf{{python {$\varheartsuit$}} :} scikit-learn, pandas,  shapely, numpy, scipy, flask, matplotlib, cython  \\ \textbf{database:} postgreSQL / postgis, mongodb, json, hdf \\ \textbf{matlab:} signal processing, optimization toolbox \\ \textbf{web:} html, javascript, d3.js  |  \textbf{general:} git, regex, linux

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}


\begin{entrylist}

%------------------------------------------------

\entry
{2013--Now}
{NYU Langone Medical Center}
{New York, NY}
{\emph{Department of Radiology}
\begin{itemize}
\item Achieved a $\sim$10x speed-up in numerical simulations by memorizing solutions to key nonhomogeneous differential equations.
\item Implemented L1-norm reconstruction algorithms that cut MRI scan time requirements by half.  
\item Developed  L-BFGS-B data fitting package for MATLAB \& Pyton/Cython that enabled the real time optimization of experimental data during MRI scans.    
\end{itemize}}

\entry
{2014--2015}
{Department of Defense -- Research Directorate}
{Washington, DC}
{\emph{Science \& Technology Policy Fellow AAAS}
\begin{itemize}
\item Secured ~\$400 million in funding commitments for research in quantum science \& technology in collaboration with the United Kingdom Ministry of Defence. 
\end{itemize}}

\entry
{2011--2013}
{University of Washington}
{Seattle, WA}
{\emph{Institute for Protein Design}
\begin{itemize}
\item Developed a hybrid Na{\"i}ve Bayes and Simulated Annealing optimization routine in C++ for the commercial protein simulation  package ROSETTA.\end{itemize}}

%------------------------------------------------

\end{entrylist}

\section{data science projects}
\textbf {{NYC Taxi Analysis}}   \href{https://cdn.rawgit.com/jfried23/nyc_taxi/1dbe38597f48650e661d613fcdb777e62b995bc7/html/chord_example/chord.html}{Tracking connectivity of NYC neighborhoods based upon taxi GPS tracking.} \\
\textbf{{Voting Conformity Web App}} scikit-learn, pandas, numpy, scipy, flask, matplotlib, cython \\
\textbf{{Science Word Cloud}} scikit-learn, pandas, numpy, scipy, flask, matplotlib, cython \\
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2005--2011}
{PhD {\normalfont Biophysics}}
{\textbf{Johns Hopkins University}}
{Authored 8 research publications (Nature, Biochemistry, JACS, \textit{et al.}) | Authored book chapter on DNA repair | Awarded patent for MRI technology.}

%------------------------------------------------

\entry
{2001--2005}
{BS {\normalfont Biochemistry \& Molecular Biology}}
{\textbf{Pennsylvania State University}}
{}

%------------------------------------------------

\end{entrylist}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2011}
{Postgraduate Scholarship}
{School of Business, The University of California}
{Awarded to the top student in their final year of a Bachelors degree. Mastered the art of filing accurate TPS reports.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{communication skills}
\textbf{{Homsite Conversion}} scikit-learn, pandas, numpy, scipy, flask, matplotlib, cython  \\
\textbf{{Voting Conformity Web App}} scikit-learn, pandas, numpy, scipy, flask, matplotlib, cython \\
\textbf{{Science Word Cloud}} scikit-learn, pandas, numpy, scipy, flask, matplotlib, cython \\
\begin{entrylist}

%------------------------------------------------

\entry
{2011}
{Oral Presentation}
{California Business Conference}
{Presented the research I conducted for my Masters of Commerce degree.}

%------------------------------------------------

\entry
{2010}
{Poster}
{Annual Business Conference, Oregon}
{As part of the course work for BUS320, I created a poster analyzing several local businesses and presented this at a conference.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} data analysis, company profiling, risk analysis, economics, web design, web app creation, software design, marketing \textbf{personal:} piano, chess, cooking, dancing, running

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}

\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

\printbibsection{book}{books} % Print all books from the bibliography

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
\end{refsection}

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
\end{refsection}

\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}